The evolution of badges of status with learners

### 2020-06-24 QD_report.Rmd
Writing the first version of the manuscript

@@

```{r fig1, echo=FALSE, fig.cap="\\label{fig:HD_game}Hawk-dove game. Dashed line is the  game theoretical prediction for frequency of hawks.", out.width = '80%'}
knitr::include_graphics("Simulations/mutType_/basicHawkDove.png")
```

@@

```{r fig2, echo=FALSE, fig.cap="\\label{fig:learning_cartoonRBF}Function approximation for the actor and the critic. Using random values for the responses of each center. Circles show the location of the centers and the maximum response they trigger, while the lines show the total response along the badge size continium.", out.width = '80%'}
knitr::include_graphics("cartoonRBF.png")
```

@@

```{r fig3, echo=FALSE, fig.cap="\\label{fig:learning_invar}Learning equilibrium when individuals do not vary in quality. Dashed line is the  game theoretical prediction for frequency of hawks.", out.width = '80%'}
knitr::include_graphics("Simulations//QualStDv_//hawkDoveLearn.png")
```

@@

```{r fig4, echo=FALSE, fig.cap="\\label{fig:learning_var0.1}Learning equilibrium when individuals vary in quality. Dashed lines are the  game theoretical predictions in the standard game.", out.width = '80%'}
knitr::include_graphics("Simulations//QualStDv_//hawkDoveLearn_0.1.png")
```

@@

```{r fig5, echo=FALSE, fig.cap="\\label{fig:learning_all_var}Effect of variation in quality for the learning equilibrium.", out.width = '80%'}
knitr::include_graphics("Simulations//QualStDv_//effectQualVariance.png")
```

@@

```{r fig6, echo=FALSE, fig.cap="\\label{fig:AC_HD}Within population variation in the learning parameters at the end of learning for three scenarios of variation in the quality of individuals.", out.width = '70%'}
knitr::include_graphics("Simulations//QualStDv_//WeightsVarQualSt.png")
```

@@

```{r fig7, echo=FALSE, fig.cap="\\label{fig:learn_dyn}Learning dynamics of the individuals in a population.", out.width = '80%'}
knitr::include_graphics("Simulations//mutType_//learnDyn200.png")
```

# How do learners fare against the "pure" strategies

@@

```{r fig8, echo=FALSE, fig.cap="\\label{fig:types_comp}Evolutionary dynamics of the learners competing against pure strategies.", out.width = '80%'}
knitr::include_graphics("Simulations//mutType_//evolDynTypes.png")
```

>>>>

<!-- # ```{r loadData, echo=FALSE,include=FALSE} -->
<!-- # Required libraries ----------------------------------------------------------- -->

<!-- library(here) -->
<!-- here() -->
<!-- source(here("AccFunc.R")) -->
<!-- # Scenario to be plotted - corresponds to folders where simulations are stored -->
<!-- scenario<-"mutType" -->
<!-- (listTest<-list.files(here("Simulations",paste0(scenario,"_")))) -->
<!-- (evolList<-grep(".txt",grep("evol",listTest,value=TRUE),value=TRUE)) -->
<!-- (indList<-grep("ind",listTest,value=TRUE)) -->

<!-- fileId<-1 -->
<!-- evol<-fread(here("Simulations",paste0(scenario,"_"),evolList[fileId])) -->
<!-- pop<-fread(here("Simulations",paste0(scenario,"_"),indList[fileId])) -->
<!-- evolStats<-evol[,.(m.freqGenHawk=mean(freqGenHawks), -->
<!--                    upIQR.freqGenHawk=fivenum(freqGenHawks)[4], -->
<!--                    lowIQR.freqGenHawk=fivenum(freqGenHawks)[2], -->
<!--                    m.freqGenDove=mean(freqGenDove), -->
<!--                    upIQR.freqGenDove=fivenum(freqGenDove)[4], -->
<!--                    lowIQR.freqGenDove=fivenum(freqGenDove)[2], -->
<!--                    m.freqEval=mean(freqGenEval), -->
<!--                    upIQR.freqGenEval=fivenum(freqGenEval)[4], -->
<!--                    lowIQR.freqGenEval=fivenum(freqGenEval)[2],  -->
<!--                    m.freqFenHawk=mean(freqFenHawks), -->
<!--                    upIQR.freqFenHawk=fivenum(freqFenHawks)[4], -->
<!--                    lowIQR.freqFenHawk=fivenum(freqFenHawks)[2], -->
<!--                    m.freqFenDove=mean(freqFenDoves), -->
<!--                    upIQR.freqFenDove=fivenum(freqFenDoves)[4], -->
<!--                    lowIQR.freqFenDove=fivenum(freqFenDoves)[2], -->
<!--                    m.meanAlpha=mean(meanAlpha), -->
<!--                    upIQR.alpha=fivenum(meanAlpha)[4], -->
<!--                    lowIQR.alpha=fivenum(meanAlpha)[2], -->
<!--                    m.meanBeta=mean(meanBeta), -->
<!--                    upIQR.beta=fivenum(meanBeta)[4], -->
<!--                    lowIQR.beta=fivenum(meanBeta)[2], -->
<!--                    m.freqHH = mean(freqHH), -->
<!--                    m.freqHD = mean(freqHD), -->
<!--                    m.freqDD = mean(freqDD), -->
<!--                    upIQR.freqHH = fivenum(freqHH)[4], -->
<!--                    upIQR.freqHD = fivenum(freqHD)[4], -->
<!--                    upIQR.freqDD = fivenum(freqDD)[4], -->
<!--                    lowIQR.freqHH = fivenum(freqHH)[4], -->
<!--                    lowIQR.freqHD = fivenum(freqHD)[2], -->
<!--                    lowIQR.freqDD = fivenum(freqDD)[2], -->
<!--                    m.weightAct_0=mean(WeightAct_0), -->
<!--                    m.weightAct_1=mean(WeightAct_1), -->
<!--                    m.weightAct_2=mean(WeightAct_2), -->
<!--                    m.weightAct_3=mean(WeightAct_3), -->
<!--                    m.weightAct_4=mean(WeightAct_4), -->
<!--                    m.weightCrit_0=mean(WeightCrit_0), -->
<!--                    m.weightCrit_1=mean(WeightCrit_1), -->
<!--                    m.weightCrit_2=mean(WeightCrit_2), -->
<!--                    m.weightCrit_3=mean(WeightCrit_3), -->
<!--                    m.weightCrit_4=mean(WeightCrit_4)),by=time] -->
<!-- # Extract means and IQR for the dynamic variables ------------------------------ -->

<!-- # popStats<-pop[, as.list(unlist(lapply(.SD, -->
<!-- #                                       function(x) list(m = mean(x), -->
<!-- #                                                        upIQR = fivenum(x)[4], -->
<!-- #                                                        downIQR = fivenum(x)[2] -->
<!-- #                                       )))), -->
<!-- #               by = time, -->
<!-- #               .SDcols=c("Quality","alpha","beta","Badge","nInteract","WeightAct_0", -->
<!-- #                         "WeightAct_1","WeightAct_2","WeightAct_3","WeightAct_4", -->
<!-- #                         "WeightCrit_0","WeightCrit_1","WeightCrit_2", -->
<!-- #                         "WeightCrit_3","WeightCrit_4")] -->

<!-- # knitr::include_graphics("Simulations/mutType_/basicHawkDove.png") -->
<!-- ``` -->

@@

<!-- ```{r fig1, echo=FALSE, fig.cap="\\label{fig:HD_game}Hawk-dove game. Dashed line is the  game theoretical prediction for frequency of hawks.", out.width = '80%'} -->
<!-- knitr::include_graphics("Simulations/mutType_/basicHawkDove.png") -->
<!-- ``` -->

@@

<!-- # ```{r fig2, echo=FALSE, fig.cap="\\label{fig:learning_cartoonRBF}Function approximation for the actor and the critic. Using random values for the responses of each center. Circles show the location of the centers and the maximum response they trigger, while the lines show the total response along the badge size continium.", out.width = '80%'} -->
<!-- # knitr::include_graphics("cartoonRBF.png") -->
<!-- ``` -->

@@

<!-- ```{r fig3, echo=FALSE, fig.cap="\\label{fig:learning_invar}Learning equilibrium when individuals do not vary in quality. Dashed line is the  game theoretical prediction for frequency of hawks.", out.width = '80%'} -->
<!-- knitr::include_graphics("Simulations//QualStDv_//hawkDoveLearn.png") -->
<!-- ``` -->

@@

<!-- ```{r fig4, echo=FALSE, fig.cap="\\label{fig:learning_var0.1}Learning equilibrium when individuals vary in quality. Dashed lines are the  game theoretical predictions in the standard game.", out.width = '80%'} -->
<!-- knitr::include_graphics("Simulations//QualStDv_//hawkDoveLearn_0.1.png") -->
<!-- ``` -->

@@

<!-- ```{r fig5, echo=FALSE, fig.cap="\\label{fig:learning_all_var}Effect of variation in quality for the learning equilibrium.", out.width = '80%'} -->
<!-- knitr::include_graphics("Simulations//QualStDv_//effectQualVariance.png") -->
<!-- ``` -->

@@

<!-- ```{r fig6, echo=FALSE, fig.cap="\\label{fig:AC_HD}Within population variation in the learning parameters at the end of learning for three scenarios of variation in the quality of individuals.", out.width = '70%'} -->
<!-- knitr::include_graphics("Simulations//QualStDv_//WeightsVarQualSt.png") -->
<!-- ``` -->

@@

<!-- ```{r fig7, echo=FALSE, fig.cap="\\label{fig:learn_dyn}Learning dynamics of the individuals in a population.", out.width = '80%'} -->
<!-- knitr::include_graphics("Simulations//mutType_//learnDyn200.png") -->
<!-- ``` -->

# How do learners fare against the "pure" strategies?

@@

<!-- ```{r fig8, echo=FALSE, fig.cap="\\label{fig:types_comp}Evolutionary dynamics of the learners competing against pure strategies.", out.width = '80%'} -->
<!-- knitr::include_graphics("Simulations//mutType_//evolDynTypes.png") -->
<!-- ``` -->

# How do learners behave when signals are honest?

<!-- ```{r fig9, echo=FALSE,fig.cap="\\label{fig:honest_learn}Actor and critic developed when signals are honest. Left panel: honest signal. Right panel: learners behavioral response ",out.width='100%',fig.show='hold'} -->
<!-- knitr::include_graphics("Simulations//learHonest_//QualStDv_//weightsVarQualSt.png") -->

<!-- ``` -->

### 2020-06-24 QD_report.tex
Writing the first version of the manuscript

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The evolution of badges of status with learners},
            pdfauthor={Andrés Quiñones},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{The evolution of badges of status with learners}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Andrés Quiñones}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
    \date{}
    \predate{}\postdate{}

\usepackage{float}

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{Simulations/mutType_/basicHawkDove} \caption{\label{fig:HD_game}Hawk-dove game. Dashed line is the  game theoretical prediction for frequency of hawks.}\label{fig:fig1}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{cartoonRBF} \caption{\label{fig:learning_cartoonRBF}Function approximation for the actor and the critic. Using random values for the responses of each center. Circles show the location of the centers and the maximum response they trigger, while the lines show the total response along the badge size continium.}\label{fig:fig2}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{Simulations//QualStDv_//hawkDoveLearn} \caption{\label{fig:learning_invar}Learning equilibrium when individuals do not vary in quality. Dashed line is the  game theoretical prediction for frequency of hawks.}\label{fig:fig3}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{Simulations//QualStDv_//hawkDoveLearn_0.1} \caption{\label{fig:learning_var0.1}Learning equilibrium when individuals vary in quality. Dashed lines are the  game theoretical predictions in the standard game.}\label{fig:fig4}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{Simulations//QualStDv_//effectQualVariance} \caption{\label{fig:learning_all_var}Effect of variation in quality for the learning equilibrium.}\label{fig:fig5}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.7\linewidth]{Simulations//QualStDv_//WeightsVarQualSt} \caption{\label{fig:AC_HD}Within population variation in the learning parameters at the end of learning for three scenarios of variation in the quality of individuals.}\label{fig:fig6}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{Simulations//mutType_//learnDyn200} \caption{\label{fig:learn_dyn}Learning dynamics of the individuals in a population.}\label{fig:fig7}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{Simulations//mutType_//evolDynTypes} \caption{\label{fig:types_comp}Evolutionary dynamics of the learners competing against pure strategies.}\label{fig:fig8}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{Simulations//learHonest_//QualStDv_//weightsVarQualSt} \caption{\label{fig:honest_learn}Actor and critic developed when signals are honest. Left panel: honest signal. Right panel: learners behavioral response }\label{fig:fig9}
\end{figure}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The evolution of badges of status with learners},
  pdfauthor={Andrés Quiñones},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{float}

\title{The evolution of badges of status with learners}
\author{Andrés Quiñones}
\date{}

@@

@@

@@

@@

@@

@@

@@

@@

@@
